---
title: "Palm_oil"
author: "Agnes M"
date: "29 février 2016"
output: html_document
---

Let's find something about palm oil.
First we have to load the data. You can find the data on [Kaggle](https://www.kaggle.com/openfoodfacts/world-food-facts)

```{r, load the data, echo = F, cache = TRUE}
path_data_food_facts <- "~/0R/world-food-facts/FoodFacts.csv"
data_food_facts <- read.csv(path_data_food_facts, na.strings = c("NA",""," "))
```

Data Food Facts is a french initiative. Most of the products are consume in France. I will take into acount these products. 

```{r, french products, cache=TRUE, results='hide'}
library(dplyr)
tbl_food_france <- 
        data_food_facts%>%
        tbl_df()%>%
        filter(grepl("France", data_food_facts$countries_en) == TRUE)
```

That is the summary of the percentage of NA's by column. 

```{r, nas1, cache = TRUE}
summary(colMeans(is.na(tbl_food_france))*100)
```

I will kept the variables which contain less than 50% of NA's

```{r, cleaning}
tbl_food_france <- tbl_food_france[, colMeans(is.na(tbl_food_france)) < 0.5]
```

That's much better, no ? 

```{r, nas2, echo=FALSE, cache = TRUE}
summary(colMeans(is.na(tbl_food_france))*100)
```

I will choose some of them. I create a new data frame called nutrition.

```{r, new df, message = FALSE}
library(dplyr)
nutrition <- 
        tbl_food_france %>% select(8,10, contains("100g"), contains("oil"), contains("nutrition"))
names(nutrition)
```

There are two nutrition scores, one from France and one from the UK. Are they different ?
Ca sert a rien ça 

```{r, nut scores, cache = TRUE, echo = FALSE}
library(ggplot2)
library(gridExtra)
i <- qplot(nutrition_score_fr_100g, data = nutrition) + 
        geom_vline(xintercept = mean(nutrition$nutrition_score_fr_100g, na.rm = T), 
                   color = "red", size = 1) +
        geom_vline(xintercept = median(nutrition$nutrition_score_fr_100g, na.rm = T), 
                   color = "blue", size = 1)

j <- qplot(nutrition_score_uk_100g, data = nutrition) + 
        geom_vline(xintercept = mean(nutrition$nutrition_score_uk_100g, na.rm = T), 
                   color = "red", size = 1) +
        geom_vline(xintercept = median(nutrition$nutrition_score_fr_100g, na.rm = T), 
                   color = "blue", size = 1)

grid.arrange(i,j, nrow = 2)
```


